---
title: "Replication"
author: "Dora Simon and Julian Langer"
date: "September 10, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Please note that I have always specified `echo=TRUE` in the chunk options, so that you can see the code. In a real document, you want that option to be false.



## Loading Libraries

Here, I load all libraries necessary for the project. I set `message = FALSE`, otherwise the document will be spammed by messages from the libraries.

```{r, message = FALSE, echo=TRUE}
library(AER)      # ivreg command
library(ivpack)   # robust and clustered standard errors
library(dplyr)    # data manipulation
library(ggplot2)  # graphs
library(tibble)   # nice dataframes
library(haven)    # dta files
library(stargazer)# tables
library(sandwich) # robust se
library(lmtest)   # for print robust
```

## Exercise 1 : Graph

### Read in Data

1. Read in `maketable2.dta` from the tidy-data folder
  - Create factor variables out of `africa`, `asia`and `other`
  - Only keep the base sample (`baseco==1`)
  
```{r}
ajr_base <- read_dta("./tidy-data/maketable2.dta") %>% 
  mutate(africa = factor(africa),
         asia = factor(asia),
         other = factor(other))  %>% 
  filter(baseco == 1) 

```  
  

### Replicate Figure 2

1. Initiate the plot
  - Average Expropriation Risk is the x axis
  - Log GDP per Capita is the y axis
2. Adjust the axis labels
3. Put a regression line in the graph
  - you can adjust the color and the size
4. Add the data points as country names
  
```{r}
ggplot(ajr_base, aes(x = avexpr, y = logpgp95)) + 
  labs(x = "Average Expropriation Risk 1985-95",
       y = "Log GDP per Capita, 1995") +
  geom_smooth(method = "lm", color = "Black", size = 0.5) + 
  geom_text(aes(label = shortnam), hjust = 0, vjust = 0, size = 3) 
```


## Exercise 2 : IV Regression

### Read in data

1. Read in `maketable4.dta` from the tidy-data folder
  - Create factor variables out of `rich4`
  - Keep only the base sample (`baseco==1`)
  
```{r}
ajr_base <- read_dta("./tidy-data/maketable4.dta") %>% 
  mutate(rich4 = factor(rich4)) %>% 
  filter(baseco == 1)
``` 

### Regressions

Do the first two regressions using the `ivreg` command.

```{r}
iv_1 <- ivreg(logpgp95 ~ avexpr | logem4, data =ajr_base)
iv_2 <- ivreg(logpgp95 ~ avexpr + lat_abst | logem4  + lat_abst, data =ajr_base)

```

### Standard Errors


Compute the robust standard errors using the `robust.se` function. Your standard errors will be in the second column.


```{r}
iv_1_se <- robust.se(iv_1)[,2]
iv_2_se <- robust.se(iv_2)[,2]
```


### Table

Display the first two regressions as a table. (hint: specify the chunk option `results=asis`)
  - for viewing the table in .Rmd, specify `type="text"`
  - for a nice output in the .pdf, specify `type="latex"`

```{r, results = 'asis'}
stargazer(iv_1, iv_2,  
          se = list(iv_1_se, iv_2_se),
          dep.var.labels = "Log GDP in 1995",
          covariate.labels = c("Expropriation Risk", "Latitude", "Constant"),
          omit.stat = "ser",
          title = "Instrumental Variable Results", 
          type = "latex")
```  

<!-- This is a comment in the normal text -->

\newpage

## Additionally: Referencing variables

I can also reference variables. For instance, the coefficient on `r names(iv_1$coefficients[2])` has the value `r iv_1$coefficients[2]`.





















